Macro Impacts

### 2016-07-21 Macro Impacts Revised.tex
Rays Parametrized in Terms of Initial Condition

We now expand the hypergeometric function to first order (the first order term is zero, so all that remains is the zeroth order term)

@@

P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k^2)\,,\\
&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k^2)\,,\\
&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k^2)\,.

@@

\pagebreak
\section{Numerical Methods}
From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere. Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$. We also insist that the tangent vector of $\vec p$ be at an angle $\alpha$ from the z axis.
\pagebreak
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.

>>>>

We now expand the hypergeometric function to second order (the first order term is zero, so all that remains is the zeroth order term)

@@

P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k)\,,\\
&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k)\,,\\
&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k)\,.

@@

\pagebreak
\section{Numerical Methods}
From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere. Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(x_0,0)$. We also insist that the tangent vector of $\vec p$ be at an angle $\alpha$ from the x axis. The parametrization in terms of these initial conditions is
\begin{align}
r(s)&=\f{a}{b}\sqrt{\f{a^2\p{e^{2abs}-1}^2+b^2\p{e^{2abs}+1}^2x_0^2+2(-1)^{s_1}ab\p{e^{4abs}-1}x_0\abs{\cos\alpha}}{a^2\p{e^{2abs}+1}^2+b^2\p{e^{2abs}-1}^2x_0^2+2(-1)^{s_1}ab\p{e^{4abs}-1}x_0\abs{\cos\alpha}}}\,,\\
\notag\theta(s)&=\arccot\ps{\f{4(-1)^{s_2}abx_0(a^2-b^2x_0^2)\sin\alpha}{4a^2b^2(1+e^{4abs})x_0^2+4(-1)^{s_2}abe^{4abs}x_0(a^2+b^2x_0^2)\cos\alpha+(e^{4abs}-1)(a^4+b^4x_0^4+2a^2b^2x_0^2\cos(2\alpha))}}-\\
&\hspace{1cm}-\arctan\ps{\f{(-1)^{s_2}(2abx_0+(-1)^{s_1}(a^2+b^2x_0^2)\cos\alpha)\csc\alpha}{a^2-b^2x_0^2}}
\end{align}
We now need to solve for
\pagebreak
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.
